Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-01-21 manuscript.tex
first draft
update / clean up
revised

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contextual recruitment of selective attention can be updated via changes in task-relevance},
            pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation,
Context-specific, Task Relevance},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

\section{Introduction}\label{introduction}

Selective attention processes are commonly investigated using
interference paradigms such as the Stroop (1935) and flanker (B. A.
Eriksen \& Eriksen, 1974) tasks, where participants identify a target
while ignoring a response-congruent or -incongruent distractor.
Performance is typically better on congruent versus incongruent trials
and the difference-the congruency effect-taken as an index of
attentional priorities. Large congruency effects are thought to reflect
ineffective filtering of the distracting stimuli whereas small
congruency effects are thought to reflect effective filtering. By
probing factors that systematically alter congruency effects, we can
then make inferences about processes that control attentional filtering.
For example, manipulating the frequency of conflict via the proportion
of congruent versus incongruent trials has shown to influence the size
of the congruency effect. Typically, a high proportion congruent
experiment produces large congruency effects, whereas a low proportion
congruent experiment produces small congruency effects (Logan \&
Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This
result is usually explained as strategic control, where participants
increase attentional control under high-conflict demands and relax
attentional control under low-conflict demands (Logan, 1980; Logan \&
Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer,
1982). Recent work however, has demonstrated that attentional control is
not only adjusted by top-down regulation, but can also be triggered
automatically by environmental cues (Brosowsky \& Crump, 2018; J. Bugg
\& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \&
Egner, 2012; Mayr \& Bryck, 2007).

@@

One explanation for CSPC effects is that the repeated application of
attentional priorities in a particular context creates an associative
link in episodic memory between the attentional control procedures and
the contextual information (Abrahamse, Braem, Notebaert, \& Verguts,
2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the
associative link is established, processing the context is assumed to
trigger the retrieval of previous experiences, automatically reinstating
the associated attentional priorities. Although this explanation seems
plausible, it remains largely unclear how such associations are
established and perhaps more importantly, it remains unclear what
determines which learned associations will be used to guide attention at
any given moment.

The importance of the latter issue becomes increasingly clear if we
speculate about context-specificity in more complex, real-world
environments. Consider myself, right now, writing this article in a
coffee shop. The coffee shop is a complex environment that contains a
multitude of contextual cues (e.g., pictures on the wall, chairs,
coffee, laptop), each of which I have had many different experiences
applying attentional control. Although my laptop might cue attentional
processing helpful for finishing this article, other features of the
coffee shop might cue other, unhelpful attentional processing related to
other experiences like socializing and people-watching. This is all to
say that our environments, and experiences within them, afford many
different associative relationships between cognitive processing and
environmental cues. What then determines which associative relationships
will be used to guide attention (or even if such associative
relationships are used at all)?

Task-relevance might be one factor that is important for establishing
and using context-attention associations. This proposal might seem
counter-intuitive as it is typically assumed that the context, within
selective attention tasks at least, is completely irrelevant to the
task. In fact, referring to such stimulus dimensions as the
\enquote{context} carries with it an implication that the feature is
background information, irrelevant to the task-at-hand, and should be
ignored by the participant. A closer look at CSPC designs however,
suggests that the context cues may not be as irrelevant as implied. For
example, the most commonly used context cue is location (Brosowsky \&
Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al.,
2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler
et al., 2018). Although in some sense, the location is irrelevant for
identifying the color of a word, it seems disingenuous to consider it
completely task-irrelevant. In order to identify the target, the
participant must first identify and orient to its location on the
screen. In this is sense, it is relevant to their ability to complete
the task and furthermore, location information may receive priority
during encoding (Logan, 1998; Mayr, 1996). Similar arguments could be
made about other context features that are inherent to processing the
target stimulus, like font-type (J. Bugg, Jacoby, \& Toth, 2008) and
color (Vietze \& Wendt, 2009).

To date, we are aware of only one study that has looked at
task-relevance within the CSPC literature. Crump, Vaquero, \& Milliken
(2008) used a Stroop prime-probe task where the distractor word is
presented first followed by a color patch probe. Critically, they used
the shape of the color patch probe, either a square or a circle, as the
contextual dimension; one associated with a high frequency of conflict,
the other with a low frequency. In one experiment participants were made
aware of the shape-proportion contingencies but given no additional
instructions. In the second, participants were given a secondary task to
count the number of trials that contained a square. The first experiment
failed to find evidence for context-specificity, whereas the second did.
Although not testing task-relevance directly, (2013)) found similar
effects. In this study they used images of male and female faces as
context cues in a flanker task. When given instructions to think of the
faces as members of the gender categories they found CSPC effects, but
when given instructions to think of the faces as individuals they did
not. These results suggest that making a context dimension relevant to
the on-going task is important for producing CSPC effects.

@@

Some prior suggests that the task-relevance of contextual information is
important for establishing new associations between context cues and
attentional priorities. Simply put, CSPC effects emerge when context
cues are somehow made relevant to the task, but do not when made
irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008). However, it
still remains unclear how task-relevance may or may not inform the use
of previously learned associations. In the current study, we examined
whether manipulating task-relevance would cause participants to ignore a
previously learned association and adopt a new context-specific control
strategy.

@@

The critical measure of interest is the congruency effect produced in
the frequency unbiased context. If, on the one hand, task-relevance has
no impact on the use of context-attention associations we would expect
no differences between the congruency effects when the high-conflict
context dimension is made task-relevant or the low-conflict context
dimension is made task-relevant. This could occur because all three
contexts are treated as individual contexts throughout the whole
experiment (e.g., Cañadas et al., 2013). Or it could occur because
associations formed in the first block interfere with learning new
associations in the second (e.g., Brosowsky \& Crump, 2016). On other
hand, task-relevance might not only dictate how associations are formed,
but also whether learned associations are used. In this case, we would
expect that there will be smaller congruency effects when the
high-conflict context dimension is made task-relevant as compared to
when the low-conflict context dimension is made task-relevant. This
would demonstrate that participants were able to ignore a previously
learned association and adopt a new context-specific control strategy.

A secondary goal was to conceptually replicate previous findings and
test the generalizability of any task-relevance effects. Therefore, we
included three conditions that differed only in the kinds of stimuli
used to create context cues. In one condition we used face images where
context dimensions were defined by social categories, similar to Cañadas
et al., (2013). However, they found that social categorization occurred
spontaneously and it was unclear what impact that would have on the
current results. Therefore, we included another condition that used
images of simple objects where context dimensions were defined by object
features. Finally, Cañadas et al.(2013) also found that context effects
generalized to novel face images. In our third condition we used
non-repeating face exemplars to examine whether any task-relevance
effects would also generalize in our design or if learning would be
image-specific.

@@

All participants were recruited from Amazon Mechanical Turk (AMT) and
compensated \$2.00 for participating. The amount compensated was
calculated by estimating the maximum amount of time required to complete
each experiment and multiplying by \$6.00 per hour. For each experiment
the number of HITs (Human intelligence tasks, an Amazon term for a
work-unit) refers to the number of participants who initiated the study.
Participants were included in the study if they completed all trials. We
posted 150 HITs and 145 participants completed all trials.

@@

Design. Experiment 1 used a 2x2x3 mixed design with task-relevant
context (0\% and 100\%) and unbiased-item congruency (congruent and
incongruent) as within-subject factors, and context-type (object,
social, and social/non-repeating) as the between-subjects factor. All
three conditions were constructed using the same general method. The
experiment was divided into two phases. Each phase consisted of 144
flanker trials (48 trials per context), and 13 count response trials for
a total of 314 trials. On the count response trials, participants
indicated how many trials they had counted until that point. The count
response trials occurred once for every 12 flanker trials and was
randomly inserted between trial 6 and 12 of each 12-trial block. Each
phase ended with one additional count response trial.

@@

All participants were AMT workers who found the experiment using the AMT
system. The participant recruitment procedure and tasks were approved by
the Brooklyn College Institutional Review Board. Each participant read a
short description of the task and gave consent by pressing a button
acknowledging they had read the displayed consent form. Participants
then completed a short demographic survey, and proceeded to the main
task, which was displayed as a pop-up window. Participants were
instructed to identify the direction of the center arrow on each trial
as quickly and accurately as possible by pressing \enquote{z} if the
arrow pointed left, and \enquote{m} if the arrow pointed right.
Additionally, they were instructed to silently keep count of the number
of trials that contained a feature. In the object context condition,
they were asked to count trials that contained a certain color (blue or
green) or object-identity (hat or chair) and in the social context
conditions they were asked to count the number of trials that contained
appeared a certain gender (male or female) or race (black or white).
Periodically throughout the experiment, participants were asked to
report how many trials they had counted until that point and to restart
their count from 0. Halfway through the experiment participants received
new instructions about which feature to count (see Figure 1C). Each
trial began with a blank inter-stimulus interval (ISI) of 400 ms,
followed by a fixation cross presented in the center of the screen for
200 ms, then a second blank ISI of 400 ms. Next, the flanker and context
stimuli appeared in the center of screen (the flanker above the context
image; see Figure 1B) and remained on screen until a response was made.
Following a response, accuracy feedback was presented for 1000 ms. A
response automatically triggered the next trial. Halfway through the
experiment (157 trials), participants received new instructions about
which feature to count and to press the button on-screen when they were
ready to continue.

@@

\begin{figure}
\centering
\includegraphics{v1-task-relevance-cspc_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
(incongruent - congruent) for frequency unbiased items in reaction times
(left) and error rates (right) as a function of the task-relevant
context (100\% proportion congruent versus 0\% proportion congruent).}
\end{figure}

@@

Similarly, the corresponding error analysis also resulted in a
significant two-way interaction between the task-relevant context and
unbiased-item congruency, \(F(1, 128) = 8.30\),
\(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\),
and a non-significant three-way interaction between task-relevant
context, unbiased-item congruency, and context-type,
\(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\),
\(\hat{\eta}^2_p = .000\). Therefore, the congruency effects in error
rates were also smaller when the context dimension associated with high
conflict was made task-relevant, corroborating the results of the
reaction time analysis.

@@

\hypertarget{ref-alards-tomalin_auditory_2017}{}
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
statistical learning: Predictive frequency information affects the
deployment of contextually mediated attentional resources on perceptual
tasks. \emph{Journal of Cognitive Psychology}, \emph{0}(0), 1--11.
doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

@@

\hypertarget{ref-brosowsky_memory-guided_2018}{}
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
attention: Single experiences with conflict have long-lasting effects on
cognitive control. \emph{Journal of Experimental Psychology: General}.
doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

@@

\hypertarget{ref-crump_context-dependent_2018}{}
Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
From Proportion Congruent Effects. \emph{Canadian Journal of
Experimental Psychology= Revue Canadienne de Psychologie Experimentale}.

@@

\hypertarget{ref-fischer_predicting_2015}{}
Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
multitasking reduces between-tasks interactions. Retrieved from
\url{http://psycnet.apa.org/psycinfo/2015-47211-001/}

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Times New Roman}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contextual recruitment of selective attention can be updated via changes in task-relevance},
            pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation,
Context-specific, Task Relevance},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{setspace}\doublespacing
\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
\setlength{\parskip}{0pt}
\raggedbottom

@@

Selective attention is commonly investigated using interference
paradigms such as the Stroop (1935) and flanker (B. A. Eriksen \&
Eriksen, 1974) tasks, where participants identify a target while
ignoring a response-congruent or -incongruent distractor. Performance is
typically better on congruent versus incongruent trials and the
difference---the congruency effect---taken as an index of attentional
priorities. Large congruency effects are thought to reflect ineffective
filtering of the distracting stimuli whereas small congruency effects
are thought to reflect effective filtering. By probing factors that
systematically alter congruency effects, we can then make inferences
about processes that control attentional filtering. For example,
manipulating the frequency of conflict via the proportion of congruent
versus incongruent trials has shown to influence the size of the
congruency effect. Typically, a high proportion congruent experiment
produces large congruency effects, whereas a low proportion congruent
experiment produces small congruency effects (Logan \& Zbrodoff, 1979;
Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually
explained as strategic control, where participants increase attentional
control under high-conflict demands and relax attentional control under
low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan,
Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work
however, has demonstrated that attentional control is not only adjusted
by top-down regulation, but can also be triggered automatically by
environmental cues (Brosowsky \& Crump, 2018; J. Bugg \& Crump, 2012;
Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012;
Mayr \& Bryck, 2007).

@@

One explanation for CSPC effects is that the repeated application of
attentional priorities in a particular context creates an associative
link in episodic memory between the attentional control procedures and
the contextual information (Abrahamse, Braem, Notebaert, \& Verguts,
2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the
associative link is established, processing the context is assumed to
trigger the retrieval of previous experiences, automatically reinstating
associated attentional priorities. As a result, automatic memory-based
retrieval allows attentional priorities to be rapidly adjusted in a
context-appropriate fashion. However, the obligatory nature of
memory-based attentional control remains unclear, in particular in
situations when multiple contextual features could be used as cues for
retrieval.

For example, real-world environments offer a plethora of context cues.
Consider writing an article in a coffee shop. The coffee shop is a
complex environment with numerous context cues (e.g., pictures on the
wall, chairs, coffee, laptop), and associated attentional priorities.
Although a laptop might cue attentional processing helpful for writing,
other features of the coffee shop might cue attentional processing
related to other experiences like socializing and people-watching. Given
that all of these cues are available to set attentional priorities, what
determines which associative relationships will be used to guide
attention? On the one hand, context-based retrieval of attentional
priorities might be completely obligatory and a writer's attention would
be at the mercy of the environment. On the other hand, there is some
evidence that contextual cuing of attention is not entirely obligatory
and can be constrained by task goals, allowing the laptop to take
priority as a contextual cue over other contextual cues that are
irrelevant to the task at hand.

Prior work shows that task-relevance is necessary for establishing and
using context-attention associations. First, the most commonly used
context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton,
2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken,
2008; Weidler \& Bugg, 2016; Weidler et al., 2018). Although in some
sense, the location is irrelevant for identifying the color of a word,
it seems disingenuous to consider it completely task-irrelevant. In
order to identify the target, the participant must first identify and
orient to its location on the screen. In this is sense, it is relevant
to their ability to complete the task and furthermore, location
information may receive priority during encoding (Logan, 1998; Mayr,
1996). Similar arguments could be made about other context features that
are inherent to processing the target stimulus, like font-type (J. Bugg,
Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).

Second, we are aware of only one study that has looked at task-relevance
within the CSPC literature. Crump, Vaquero, \& Milliken (2008) used a
Stroop prime-probe task where the distractor word is presented first
followed by a color patch probe. Critically, they used the shape of the
color patch probe, either a square or a circle, as the contextual
dimension; one associated with a high frequency of conflict, the other
with a low frequency. In one experiment participants were made aware of
the shape-proportion contingencies but given no additional instructions.
In the second, participants were given a secondary task to count the
number of trials that contained a square. The first experiment failed to
find evidence for context-specificity, whereas the second did. Although
not testing task-relevance directly, Cañadas, Rodríguez-Bailón,
Milliken, and Lupiáñez (2013){]} found similar effects. In this study
they used images of male and female faces as context cues in a flanker
task. When given instructions to think of the faces as members of the
gender categories they found CSPC effects, but when given instructions
to think of the faces as individuals they did not. These results suggest
that making a context dimension relevant to the on-going task is
important for producing CSPC effects.

@@

Prior work suggests that the task-relevance of contextual information is
important for establishing new associations between context cues and
attentional priorities. Simply put, CSPC effects emerge when context
cues are somehow made relevant to the task, but do not when made
irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008). However, it
still remains unclear how task-relevance may or may not inform the use
of previously learned associations. In the current study, we examined
whether manipulating task-relevance would cause participants to ignore a
previously learned association and adopt a new context-specific control
strategy.

@@

The critical measure of interest is the congruency effect produced in
the frequency unbiased context. If, on the one hand, task-relevance has
no impact on the use of context-attention associations we would expect
no differences between the congruency effects when the high-conflict
context dimension is made task-relevant or the low-conflict context
dimension is made task-relevant. This could occur because all three
contexts are treated as individual contexts throughout the whole
experiment (e.g., Cañadas et al., 2013). Or it could occur because
associations formed in the first block interfere with learning new
associations in the second (e.g., Brosowsky \& Crump, 2016). On other
hand, task-relevance might not only dictate how associations are formed,
but also whether learned associations are used. In this case, we would
expect smaller congruency effects when the high-conflict context
dimension is made task-relevant as compared to when the low-conflict
context dimension is made task-relevant. This would demonstrate that
participants were able to ignore a previously learned association and
adopt a new context-specific control strategy.

A secondary goal was to conceptually replicate previous findings and
test the generalizability of any task-relevance effects. Therefore, we
included three conditions that differed only in the kinds of stimuli
used to create context cues. In one condition we used face images where
context dimensions were defined by social categories, similar to Cañadas
et al. (2013). However, they found that social categorization occurred
spontaneously and it was unclear what impact that would have on the
current results. Therefore, we included another condition that used
images of simple objects where context dimensions were defined by object
features. Finally, Cañadas et al. (2013) also found that context effects
generalized to novel face images. In our third condition we used
non-repeating face exemplars to examine whether any task-relevance
effects would also generalize in our design or if learning would be
image-specific.

@@

All participants were recruited from Amazon Mechanical Turk (AMT) and
compensated \$2.00 for participating. The amount compensated was
calculated by estimating the maximum amount of time required to complete
each experiment and multiplying by \$6.00 per hour. For each experiment
the number of HITs (Human intelligence tasks, an Amazon term for a
work-unit) refers to the number of participants who initiated the study.
Participants were included in the study if they completed all trials. We
posted 150 HITs and 144 participants completed all trials.

@@

\subsection{Design}\label{design}

Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\%
and 100\%) and unbiased-item congruency (congruent and incongruent) as
within-subject factors, and context-type (object, social, and
social/non-repeating) as the between-subjects factor. All three
conditions were constructed using the same general method. The
experiment was divided into two phases. Each phase consisted of 144
flanker trials (48 trials per context), and 13 count response trials for
a total of 314 trials. On the count response trials, participants
indicated how many trials they had counted until that point. The count
response trials occurred once for every 12 flanker trials and was
randomly inserted between trial 6 and 12 of each 12-trial block. Each
phase ended with one additional count response trial.

@@

All participants were AMT workers who found the experiment using the AMT
system. The participant recruitment procedure and tasks were approved by
the Brooklyn College Institutional Review Board. Each participant read a
short description of the task and gave consent by pressing a button
acknowledging they had read the displayed consent form. Participants
then completed a short demographic survey, and proceeded to the main
task, which was displayed as a pop-up window. Participants were
instructed to identify the direction of the center arrow on each trial
as quickly and accurately as possible by pressing \enquote{z} if the
arrow pointed left, and \enquote{m} if the arrow pointed right.
Additionally, they were instructed to silently keep count of the number
of trials that contained a feature. In the object context condition,
they were asked to count trials that contained a certain color (blue or
green) or object-identity (hat or chair) and in the social context
conditions they were asked to count the number of trials that contained
appeared a certain gender (male or female) or race (black or white).
Periodically throughout the experiment, participants were asked to
report how many trials they had counted until that point and to restart
their count from 0. Halfway through the experiment participants received
new instructions about which feature to count (see Figure 1C).

Each trial began with a blank inter-stimulus interval (ISI) of 400 ms,
followed by a fixation cross presented in the center of the screen for
200 ms, then a second blank ISI of 400 ms. Next, the flanker and context
stimuli appeared in the center of screen (the flanker above the context
image; see Figure 1B) and remained on screen until a response was made.
Following a response, accuracy feedback was presented for 1000 ms. A
response automatically triggered the next trial.

Halfway through the experiment (157 trials), participants received new
instructions about which feature to count and to press the button
on-screen when they were ready to continue.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
(incongruent - congruent) for frequency unbiased items in reaction times
(left) and error rates (right) as a function of the task-relevant
context (100\% proportion congruent versus 0\% proportion congruent).}
\end{figure}

@@

@@

Similarly, the corresponding error analysis also resulted in a
significant two-way interaction between the task-relevant context and
unbiased-item congruency, \(F(1, 128) = 6.72\),
\(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a
non-significant three-way interaction between task-relevant context,
unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\),
\(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
Therefore, the congruency effects in error rates were also smaller when
the context dimension associated with high conflict was made
task-relevant, corroborating the results of the reaction time analysis.

\begin{table}[htbp]
\caption{Reaction times and error rates from Experiment 1.}
\label{TR_table}
\centering
\begin{tabular}{lllcccc}
\toprule
 & & & \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
\cmidrule(rl){4-5}
\cmidrule(rl){6-7}
\multicolumn{1}{c}{Task-Relevant Context} & \multicolumn{1}{c}{Condition} & \multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
\midrule
\multirow{9}{*}{100\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{693 (26)} & \multicolumn{1}{l}{4.17 (0.73)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{585 (23)} & \multicolumn{1}{l}{0.74 (0.27)} & \multicolumn{1}{l}{675 (28)} & \multicolumn{1}{l}{4.81 (0.82)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{587 (25)} & \multicolumn{1}{l}{0.69 (0.23)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\cmidrule(rl){2-7}
& \multirow{3}{*}{Social} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{c}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{745 (25)} & \multicolumn{1}{l}{5.86 (0.77)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{612 (21)} & \multicolumn{1}{l}{0.39 (0.19)} & \multicolumn{1}{l}{722 (26)} & \multicolumn{1}{l}{6.78 (1.04)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{616 (20)} & \multicolumn{1}{l}{0.63 (0.2)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\cmidrule(rl){2-7}
& \multirow{3}{*}{Social (NR)} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{813 (25)} & \multicolumn{1}{l}{5.04 (0.74)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{689 (23)} & \multicolumn{1}{l}{0.19 (0.14)} & \multicolumn{1}{l}{793 (27)} & \multicolumn{1}{l}{5.72 (1.06)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{689 (25)} & \multicolumn{1}{l}{0.48 (0.17)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
\multirow{9}{*}{0\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{649 (16)} & \multicolumn{1}{l}{3.84 (0.6)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{587 (17)} & \multicolumn{1}{l}{0.56 (0.21)} & \multicolumn{1}{l}{657 (17)} & \multicolumn{1}{l}{4.17 (1.02)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{634 (18)} & \multicolumn{1}{l}{2.69 (0.58)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\cmidrule(rl){2-7}
& \multirow{3}{*}{Social} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{722 (23)} & \multicolumn{1}{l}{5.77 (0.92)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{633 (20)} & \multicolumn{1}{l}{0.78 (0.5)} & \multicolumn{1}{l}{722 (25)} & \multicolumn{1}{l}{4.75 (0.9)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{673 (21)} & \multicolumn{1}{l}{1.84 (0.47)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\cmidrule(rl){2-7}
& \multirow{3}{*}{Social (NR)} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{807 (26)} & \multicolumn{1}{l}{4.55 (0.8)} \\
& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{735 (28)} & \multicolumn{1}{l}{0.87 (0.36)} & \multicolumn{1}{l}{818 (30)} & \multicolumn{1}{l}{4.26 (0.8)} \\
& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{779 (34)} & \multicolumn{1}{l}{2.03 (0.4)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
 & & & & & & \\
\bottomrule
\multicolumn{7}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\%); PC = Proportion Congruent;} \\
\multicolumn{7}{l}{NR = Non-Repeating; Standard Errors are presented in parantheses.} \\
\end{tabular}%
\end{table}

@@

\hypertarget{ref-alards-tomalin_auditory_2017}{}
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
statistical learning: Predictive frequency information affects the
deployment of contextually mediated attentional resources on perceptual
tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

@@

\hypertarget{ref-brosowsky_memory-guided_2018}{}
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
attention: Single experiences with conflict have long-lasting effects on
cognitive control. \emph{Journal of Experimental Psychology: General},
\emph{147}, 1134--1153.
doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

@@

\hypertarget{ref-crump_context-dependent_2018}{}
Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
From Proportion Congruent Effects. \emph{Canadian Journal of
Experimental Psychology= Revue Canadienne de Psychologie Experimentale},
\emph{74}, 91--104.

@@

\hypertarget{ref-fischer_predicting_2015}{}
Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
multitasking reduces between-tasks interactions., \emph{41}, 1482--1487.
Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
